Contrast Set Learning using WHAT

### 2015-04-05 manuscript.tex
Updates from ShareLaTeX

In order to assess the performance of the planner for the defect data set, we use the Cliffs Delta score to measure the probability that the number of bugs in test data before applying the planner is larger than after. In other words, we use the delta score to measure the ability of the planner to effective reduce the number of defects.

>>>>

In order to assess the performance of the planner for the defect data set, we use the Cliffs Delta score to measure the probability that the number of bugs in test data before applying the planner is larger than after doing so. In other words, we use the delta score to measure the ability of the planner to effective reduce the number of defects.
